Model LF

### 2022-12-17 paper version 2.Rmd
Commit

@@

# Simulate

```{r}
# In-sample prediction (no add factors)
S_model <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                   )
```

# Tjek

Plots for paper

@@

```{r}
plot(((yk_ds_01 - yk_ds_bs1) / yk_ds_bs1)*100, col= "blue", xlab= "Year", ylab= "% Change in GDP", main= "GDP", ylim= c(-0.13, 0.06));
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2)*100, col= "green");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3)*100, col= "red");
legend("top", legend=c("All channels","Except LF Channel", "Except LF and Wage channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green","red"));
grid()
```

```{r}
plot(((nl_g_01 - nl_g_bs1)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending", ylim= c(-500, 2500));
lines(((nl_g_02 - nl_g_bs2)), col= "green");
lines(((nl_g_03 - nl_g_bs3)), col= "red");
legend("left", legend=c("All channels","Except LF Channel", "Except LF and Wage channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green","red"));
grid()
```

```{r}
plot(((unemp_01 - unemp_bs1)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Sensitivity of Unemployment", ylim= c(-300,3000));
lines(((unemp_02 - unemp_bs2)*1000), col= "green");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "red");
legend("left", legend=c("All channels","Except LF Channel", "Except LF and Wage channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "red", "green"));
grid()
```

@@

## Bayli-Chetty function

>>>>

# Model data

@@

# Baselines

@@

```{r, fig.width=10, fig.height=5}

par(mfrow=c(1,2))
plot(((yk_ds_01 - yk_ds_bs1) / yk_ds_bs1)*100, col= "blue", xlab= "Year", ylab= "% Change in GDP", main= "GDP", ylim= c(-0.13, 0.06));
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2)*100, col= "green");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3)*100, col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green","red"));
grid()

plot(((nl_g_01 - nl_g_bs1)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending", ylim= c(-500, 2500));
lines(((nl_g_02 - nl_g_bs2)), col= "green");
lines(((nl_g_03 - nl_g_bs3)), col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green","red"));
grid()
```

```{r}
plot(((unemp_01 - unemp_bs1)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Unemployment", ylim= c(-300,3000));
lines(((unemp_02 - unemp_bs2)*1000), col= "green");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "green", "red"));
grid()
```

@@

# Bayli-Chetty function
